---
title: "PSEI"
output: pdf_document
---
# Packages

Load the packages.

```{r}
library(forecast)
library(ggplot2)
library(readr)
```

# Viewing and Decomposing the Data

This commant will let us view the plot of the PSEI time series

```{r}
PSEI <- read_csv("~/R/SPP/CSV/PSEI.csv", col_types = cols(Week = col_date(format = "%Y-%m-%d")))
psei <- ts(PSEI[,2], freq=365.25/7, start=2015+226/365.25)
psei %>%
  autoplot()
```

This will show the trend, seasonal, and random component of the time series.

```{r}
plot(decompose(psei))
```

# Forecasting

This is a validation of last week's forecast.

```{r}
training_psei <- subset(psei, end=length(psei)-1)
test_psei <- subset(psei, start=length(psei)-1)
fc_training_psei<-forecast(training_psei)
fc_training_psei %>%
  forecast(h=26) %>%
  autoplot() +autolayer(test_psei)
```

These are the point forecast, the 80% and the 95% confidence interval.

```{r}
fc_training_psei
```

This is next week's forecast.

```{r}
fc_psei<-forecast(psei)
fc_psei %>%
  forecast(h=40) %>%
  autoplot()
```

These are the point forecast, the 80% and the 95% confidence interval.

```{r}
fc_psei
```
This will show the tail (last 5 data points), minimum, maximum, and which entry is the minimum.

```{r}
tail(psei)
min(psei)
max(psei)
which.min(psei)
```

# ARIMA

This is a command for auto arima.

```{r}
bestfit_psei <- list(aicc=Inf)
for(i in 1:25)
{
  fit_psei <- auto.arima(psei, xreg=fourier(psei, K=i), seasonal=FALSE)
  if(fit_psei$aicc < bestfit_psei$aicc)
    bestfit_psei <- fit_psei
  else break;
}
```

The summary of the ARIMA model.

```{r}
summary(bestfit_psei)
```

The plot of the ARIMA model.

```{r}
fc_arima_psei <- forecast(bestfit_psei, xreg=fourier(psei, K=2, h=26))
plot(fc_arima_psei)
```

These are the point forecast, the 80% and the 95% confidence interval.

```{r}
fc_arima_psei
```

# Manual ARIMA

This will generate 12 arima models.

```{r}
fit_psei1 <- auto.arima(psei, xreg=fourier(psei, K=1), seasonal=FALSE)
fit_psei2 <- auto.arima(psei, xreg=fourier(psei, K=2), seasonal=FALSE)
fit_psei3 <- auto.arima(psei, xreg=fourier(psei, K=3), seasonal=FALSE)
fit_psei4 <- auto.arima(psei, xreg=fourier(psei, K=4), seasonal=FALSE)
fit_psei5 <- auto.arima(psei, xreg=fourier(psei, K=5), seasonal=FALSE)
fit_psei6 <- auto.arima(psei, xreg=fourier(psei, K=6), seasonal=FALSE)
fit_psei7 <- auto.arima(psei, xreg=fourier(psei, K=7), seasonal=FALSE)
fit_psei8 <- auto.arima(psei, xreg=fourier(psei, K=8), seasonal=FALSE)
fit_psei9 <- auto.arima(psei, xreg=fourier(psei, K=9), seasonal=FALSE)
fit_psei10 <- auto.arima(psei, xreg=fourier(psei, K=10), seasonal=FALSE)
fit_psei11 <- auto.arima(psei, xreg=fourier(psei, K=11), seasonal=FALSE)
fit_psei12 <- auto.arima(psei, xreg=fourier(psei, K=12), seasonal=FALSE)
```

This will plot the AIC of the 12 ARIMA models.

```{r}
aics<-c(AIC(fit_psei1),AIC(fit_psei2),AIC(fit_psei3),AIC(fit_psei4),AIC(fit_psei5),AIC(fit_psei6),AIC(fit_psei7),AIC(fit_psei8),AIC(fit_psei9),AIC(fit_psei10),AIC(fit_psei11),AIC(fit_psei12))
plot(aics)
```

This is the plot of the 1st ARIMA model.

```{r}
fc_psei1 <- forecast(fit_psei1, xreg=fourier(psei, K=1, h=26))
plot(fc_psei1)
```

These are the point forecast, the 80% and the 95% confidence interval.

```{r}
fc_psei1
```

# Accuray Measures

These are the accuracy measures for each model.

```{r}
accuracy(fc_psei)
```

```{r}
accuracy(fc_arima_psei)
```

```{r}
accuracy(fc_psei1)
```