---
title: "Stock Price Forecasting"
author: "Aileene Derilo"
format: html
editor: visual
---

# Background

The stock market is a group of buyers and sellers of securities that is separated into private, open, and mixed ownership stock exchanges. It is the foundation of every economy, and the main goals of any investment in the stock market are to maximize profits and reduce risks . As a result, nations must improve their stock markets since they are linked to economic progress.

Investing in the stock market could lead to a quick return on investment; therefore, stock market forecasting is one of the best strategies to achieve a profit. Technically speaking, R is a great fit for stock and investing analysis. To assess stocks and investments, this project makes use of basic R as well as the quantmod and ggplot2 libraries.

# (SSP Data)

```{r}
library(forecast)
library(ggplot2)
library(readr)
library(zoo)
```

```{r}
SSP <- read_csv("/cloud/project/CSV/SSP.csv", col_types = cols(Week = col_date(format = "%Y-%m-%d")))
SSP <- ts(SSP[,2], freq=365.25/7, start=2021+15/365.25)
SSP %>%
  autoplot()
```

```{r}
SSP_decomp <- decompose(na.locf(SSP), type="additive")
autoplot(SSP_decomp)
```

```{r}
training_SSP <- subset(SSP, end=length(SSP)-8)
test_SSP <- subset(SSP, start=length(SSP)-8)
fc_training_SSP <- forecast(training_SSP)
fc_training_SSP %>%
  forecast(h=60) %>%
  autoplot() +autolayer(test_SSP)

```

```{r}
fc_SSP <-forecast(SSP)
fc_SSP %>%
  forecast(h=20) %>%
  autoplot()
```

```{r}
fc_SSP
```

```{r}
tail(SSP)
min(SSP)
max(SSP)
which.min(SSP)
```

```{r}
bestfit_SSP <- list(aicc=Inf)
for(i in 1:25)
{
  fit_SSP <- auto.arima(SSP, xreg=fourier(SSP, K=i), seasonal=FALSE)
  if(fit_SSP$aicc < bestfit_SSP$aicc)
    bestfit_SSP <- fit_SSP
  else break;
}
```

```{r}
summary(bestfit_SSP)
```

```{r}
fc_arima_SSP <- forecast(bestfit_SSP, xreg=fourier(SSP, K=1, h=26))
plot(fc_arima_SSP)
```

```{r}
fit_SSP1 <- auto.arima(SSP, xreg=fourier(SSP, K=1), seasonal=FALSE)
fit_SSP2 <- auto.arima(SSP, xreg=fourier(SSP, K=2), seasonal=FALSE)
fit_SSP3 <- auto.arima(SSP, xreg=fourier(SSP, K=3), seasonal=FALSE)
fit_SSP4 <- auto.arima(SSP, xreg=fourier(SSP, K=4), seasonal=FALSE)
fit_SSP5 <- auto.arima(SSP, xreg=fourier(SSP, K=5), seasonal=FALSE)
fit_SSP6 <- auto.arima(SSP, xreg=fourier(SSP, K=6), seasonal=FALSE)
fit_SSP7 <- auto.arima(SSP, xreg=fourier(SSP, K=7), seasonal=FALSE)
fit_SSP8 <- auto.arima(SSP, xreg=fourier(SSP, K=8), seasonal=FALSE)
fit_SSP9 <- auto.arima(SSP, xreg=fourier(SSP, K=9), seasonal=FALSE)
fit_SSP10 <- auto.arima(SSP, xreg=fourier(SSP, K=10), seasonal=FALSE)
fit_SSP11 <- auto.arima(SSP, xreg=fourier(SSP, K=11), seasonal=FALSE)
fit_SSP12 <- auto.arima(SSP, xreg=fourier(SSP, K=12), seasonal=FALSE)
```

```{r}
aics<-c(AIC(fit_SSP1),AIC(fit_SSP2),AIC(fit_SSP3),AIC(fit_SSP4),AIC(fit_SSP5),AIC(fit_SSP6),AIC(fit_SSP7),AIC(fit_SSP8),AIC(fit_SSP9),AIC(fit_SSP10),AIC(fit_SSP11),AIC(fit_SSP12))
plot(aics)
```

```{r}
fc_arima_man_SSP <- forecast(fit_SSP1, xreg=fourier(SSP, K=1, h=26))
plot(fc_arima_man_SSP)
```

```{r}
fc_arima_man_SSP
```

```{r}
accuracy(fc_SSP)
```

```{r}
accuracy(fc_arima_SSP)
```

```{r}
accuracy(fc_arima_man_SSP)
```

# (TECH Data)

```{r}
TECH <- read_csv("/cloud/project/CSV/TECH.csv", col_types = cols(Week = col_date(format = "%Y-%m-%d")))
TECH <- ts(TECH[,2], freq=365.25/7, start=2021+15/365.25)
TECH %>%
  autoplot()
```

```{r}
TECH_decomp <- decompose(na.locf(SSP), type="additive")
autoplot(TECH_decomp)
```

```{r}
training_TECH <- subset(TECH, end=length(TECH)-8)
test_TECH <- subset(TECH, start=length(TECH)-8)
fc_training_TECH <- forecast(training_TECH)
fc_training_TECH %>%
  forecast(h=60) %>%
  autoplot() +autolayer(test_TECH)
```

```{r}
fc_TECH <-forecast(TECH)
fc_TECH %>%
  forecast(h=20) %>%
  autoplot()
```

```{r}
fc_TECH
```

```{r}
tail(TECH)
min(TECH)
max(TECH)
which.min(TECH)
```

```{r}
bestfit_TECH <- list(aicc=Inf)
for(i in 1:25)
{
  fit_TECH <- auto.arima(TECH, xreg=fourier(TECH, K=i), seasonal=FALSE)
  if(fit_TECH$aicc < bestfit_TECH$aicc)
    bestfit_TECH <- fit_TECH
  else break;
}
```

```{r}
summary(bestfit_TECH)
```

```{r}
fc_arima_TECH <- forecast(bestfit_TECH, xreg=fourier(TECH, K=1, h=26))
plot(fc_arima_TECH)
```

```{r}
fit_TECH1 <- auto.arima(TECH, xreg=fourier(TECH, K=1), seasonal=FALSE)
fit_TECH2 <- auto.arima(TECH, xreg=fourier(TECH, K=2), seasonal=FALSE)
fit_TECH3 <- auto.arima(TECH, xreg=fourier(TECH, K=3), seasonal=FALSE)
fit_TECH4 <- auto.arima(TECH, xreg=fourier(TECH, K=4), seasonal=FALSE)
fit_TECH5 <- auto.arima(TECH, xreg=fourier(TECH, K=5), seasonal=FALSE)
fit_TECH6 <- auto.arima(TECH, xreg=fourier(TECH, K=6), seasonal=FALSE)
fit_TECH7 <- auto.arima(TECH, xreg=fourier(TECH, K=7), seasonal=FALSE)
fit_TECH8 <- auto.arima(TECH, xreg=fourier(TECH, K=8), seasonal=FALSE)
fit_TECH9 <- auto.arima(TECH, xreg=fourier(TECH, K=9), seasonal=FALSE)
fit_TECH10 <- auto.arima(TECH, xreg=fourier(TECH, K=10), seasonal=FALSE)
fit_TECH11 <- auto.arima(TECH, xreg=fourier(TECH, K=11), seasonal=FALSE)
fit_TECH12 <- auto.arima(TECH, xreg=fourier(TECH, K=12), seasonal=FALSE)
```

```{r}
aics<-c(AIC(fit_TECH1),AIC(fit_TECH2),AIC(fit_TECH3),AIC(fit_TECH4),AIC(fit_TECH5),AIC(fit_TECH6),AIC(fit_TECH7),AIC(fit_TECH8),AIC(fit_TECH9),AIC(fit_TECH10),AIC(fit_TECH11),AIC(fit_TECH12))
plot(aics)
```

```{r}
fc_arima_man_TECH <- forecast(fit_TECH1, xreg=fourier(TECH, K=1, h=26))
plot(fc_arima_man_TECH)
```

```{r}
fc_arima_man_TECH
```

```{r}
accuracy(fc_TECH)
```

```{r}
accuracy(fc_arima_TECH)
```

```{r}
accuracy(fc_arima_man_TECH)
```

# (SSI Data)

```{r}
SSI <- read_csv("/cloud/project/CSV/SSI.csv", col_types = cols(Week = col_date(format = "%Y-%m-%d")))

SSI <- ts(SSI[,2], freq=365.25/7, start=2021+15/365.25)

SSI %>%

  autoplot()
```

```{r}
SSI_decomp <- decompose(na.locf(SSI), type="additive")

autoplot(SSI_decomp)
```

```{r}
training_SSI <- subset(SSI, end=length(SSI)-8)

test_SSI <- subset(SSI, start=length(SSI)-8)

fc_training_SSI <- forecast(training_SSI)

fc_training_SSI %>%

  forecast(h=60) %>%

  autoplot() +autolayer(test_SSI)
```

```{r}
fc_SSI <-forecast(SSI)

fc_SSI %>%

  forecast(h=20) %>%

  autoplot()
```

```{r}
fc_SSI
```

```{r}
tail(SSI)

min(SSI)

max(SSI)

which.min(SSI)
```

```{r}
bestfit_SSI <- list(aicc=Inf)

for(i in 1:25)

{

  fit_SSI <- auto.arima(SSI, xreg=fourier(SSI, K=i), seasonal=FALSE)

  if(fit_SSI$aicc < bestfit_SSI$aicc)

    bestfit_SSI <- fit_SSI

  else break;

}
```

```{r}
summary(bestfit_SSI)
```

```{r}
fc_arima_SSI <- forecast(bestfit_SSI, xreg=fourier(SSI, K=1, h=26))

plot(fc_arima_SSI)
```

```{r}
fit_SSI1 <- auto.arima(SSI, xreg=fourier(SSI, K=1), seasonal=FALSE)

fit_SSI2 <- auto.arima(SSI, xreg=fourier(SSI, K=2), seasonal=FALSE)

fit_SSI3 <- auto.arima(SSI, xreg=fourier(SSI, K=3), seasonal=FALSE)

fit_SSI4 <- auto.arima(SSI, xreg=fourier(SSI, K=4), seasonal=FALSE)

fit_SSI5 <- auto.arima(SSI, xreg=fourier(SSI, K=5), seasonal=FALSE)

fit_SSI6 <- auto.arima(SSI, xreg=fourier(SSI, K=6), seasonal=FALSE)

fit_SSI7 <- auto.arima(SSI, xreg=fourier(SSI, K=7), seasonal=FALSE)

fit_SSI8 <- auto.arima(SSI, xreg=fourier(SSI, K=8), seasonal=FALSE)

fit_SSI9 <- auto.arima(SSI, xreg=fourier(SSI, K=9), seasonal=FALSE)

fit_SSI10 <- auto.arima(SSI, xreg=fourier(SSI, K=10), seasonal=FALSE)

fit_SSI11 <- auto.arima(SSI, xreg=fourier(SSI, K=11), seasonal=FALSE)

fit_SSI12 <- auto.arima(SSI, xreg=fourier(SSI, K=12), seasonal=FALSE)
```

```{r}
aics<-c(AIC(fit_SSI1),AIC(fit_SSI2),AIC(fit_SSI3),AIC(fit_SSI4),AIC(fit_SSI5),AIC(fit_SSI6),AIC(fit_SSI7),AIC(fit_SSI8),AIC(fit_SSI9),AIC(fit_SSI10),AIC(fit_SSI11),AIC(fit_SSI12))
plot(aics)
```

```{r}
fc_arima_man_SSI <- forecast(fit_SSI1, xreg=fourier(SSI, K=1, h=26))

plot(fc_arima_man_SSI)
```

```{r}
fc_arima_man_SSI
```

```{r}
accuracy(fc_SSI)
```

```{r}
accuracy(fc_arima_SSI)
```

```{r}
accuracy(fc_arima_man_SSI)
```

# (SMC Data)

```{r}
SMC <- read_csv("/cloud/project/CSV/SMC.csv", col_types = cols(Week = col_date(format = "%Y-%m-%d")))

SMC <- ts(SMC[,2], freq=365.25/7, start=2021+15/365.25)

SMC %>%

  autoplot()
```

```{r}
SMC_decomp <- decompose(na.locf(SMC), type="additive")

autoplot(SMC_decomp)
```

```{r}
training_SMC <- subset(SMC, end=length(SMC)-8)

test_SMC <- subset(SMC, start=length(SMC)-8)

fc_training_SMC <- forecast(training_SMC)

fc_training_SMC %>%

  forecast(h=60) %>%

  autoplot() +autolayer(test_SMC)
```

```{r}
fc_SMC <-forecast(SMC)

fc_SMC %>%

  forecast(h=20) %>%

  autoplot()
```

```{r}
fc_SMC
```

```{r}
tail(SMC)

min(SMC)

max(SMC)

which.min(SMC)
```

```{r}
bestfit_SMC <- list(aicc=Inf)

for(i in 1:25)

{

  fit_SMC <- auto.arima(SMC, xreg=fourier(SMC, K=i), seasonal=FALSE)

  if(fit_SMC$aicc < bestfit_SMC$aicc)

    bestfit_SMC <- fit_SMC

  else break;

}
```

```{r}
summary(bestfit_SMC)
```

```{r}
fc_arima_SMC <- forecast(bestfit_SMC, xreg=fourier(SMC, K=1, h=26))

plot(fc_arima_SMC)
```

```{r}
fit_SMC1 <- auto.arima(SMC, xreg=fourier(SMC, K=1), seasonal=FALSE)

fit_SMC2 <- auto.arima(SMC, xreg=fourier(SMC, K=2), seasonal=FALSE)

fit_SMC3 <- auto.arima(SMC, xreg=fourier(SMC, K=3), seasonal=FALSE)

fit_SMC4 <- auto.arima(SMC, xreg=fourier(SMC, K=4), seasonal=FALSE)

fit_SMC5 <- auto.arima(SMC, xreg=fourier(SMC, K=5), seasonal=FALSE)

fit_SMC6 <- auto.arima(SMC, xreg=fourier(SMC, K=6), seasonal=FALSE)

fit_SMC7 <- auto.arima(SMC, xreg=fourier(SMC, K=7), seasonal=FALSE)

fit_SMC8 <- auto.arima(SMC, xreg=fourier(SMC, K=8), seasonal=FALSE)

fit_SMC9 <- auto.arima(SMC, xreg=fourier(SMC, K=9), seasonal=FALSE)

fit_SMC10 <- auto.arima(SMC, xreg=fourier(SMC, K=10), seasonal=FALSE)

fit_SMC11 <- auto.arima(SMC, xreg=fourier(SMC, K=11), seasonal=FALSE)

fit_SMC12 <- auto.arima(SMC, xreg=fourier(SMC, K=12), seasonal=FALSE)
```

```{r}
aics<-c(AIC(fit_SMC1),AIC(fit_SMC2),AIC(fit_SMC3),AIC(fit_SMC4),AIC(fit_SMC5),AIC(fit_SMC6),AIC(fit_SMC7),AIC(fit_SMC8),AIC(fit_SMC9),AIC(fit_SMC10),AIC(fit_SMC11),AIC(fit_SMC12))

plot(aics)
```

```{r}
fc_arima_man_SMC <- forecast(fit_SMC1, xreg=fourier(SMC, K=1, h=26))

plot(fc_arima_man_SMC)
```

```{r}
fc_arima_man_SMC
```

```{r}
accuracy(fc_SMC)
```

```{r}
accuracy(fc_arima_SMC)
```

```{r}
accuracy(fc_arima_man_SMC)
```
